%\documentclass[11pt]{book}
%\usepackage{palatino}
%\usepackage{amsfonts,amsmath,amssymb}
%
%\begin{document}
%\pagestyle{empty}
%{\noindent\bf Spring 2022 \hfill Firstname M.~Lastname}
%\vskip 16pt
%\centerline{\bf University of Central Florida}
%\centerline{\bf College of Business}
%\vskip 16pt
%\centerline{\bf QMB 6912}
%\centerline{\bf Capstone Project in Business Analytics}
%\vskip 10pt
%\centerline{\bf Solutions:  Problem Sets \#1 \& 2}
%\vskip 32pt
%
%This example has sections for each article in Problem Set \#1.

\section{Introduction}

In this paper I analyze the prices of fly reels. 
My aim is to investigate the value of fly reels produced in different locations.
Does there exist a Made-in-America premium? 
If so, how large is it?
Does the premium depend on the characteristics of the fly reels?
% 
The answers to these questions can be applied to the 
operational decisions of fly reel manufacturers.
In particular, this analysis can be used to make recommendations
on whether fly reels should be made in America or produced overseas. 
% 

In the following pages, I will investigate these questions and
ultimately fit a model for the price of fly reels, 
allowing for endogeneity in the choice of the
characteristics of fly reels 
and the location in which they are manufacturers
produced and sold by each manufacturer. 
To understand the dynamics of a sample selection model, 
it is worthwhile to understand the research related to these questions. 



\section{Economic Theory}

\subsection{Market for Lemons}


Akerlof's description of the market for lemons is a long-standing contribution to the understanding of asymmetric information. 


\subsection{Characteristic Theory}

The paper by Lancaster (1966) is a contribution to economic theory in which he makes the case for a sound theory of consumer choice, 
in which the consumer's preferences are defined on the characteristics of different goods, 
rather than the quantities of uniformly-defined goods.


\subsection{Hedonic Pricing Models}

Rosen (1974) builds on the work of Lancaster (1966)
by providing an empirical framework for estimating the value
of products based on their characteristics. 




\section{Empirical Framework}

\subsection{Tobit Models}

Heckman (1979) described sample selection models as a model specification question. 

Amemiya (1984) summarized the variaous types of Tobit models
and provides a review of research with applications of these models. 

Lee and Trost (1978) is a well-known application to housing markets, 
which incorporates the fact that the residents make a decision
to either own or rent a home before buying. 


% \end{document}