%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\documentclass[11pt]{article}
\usepackage{fullpage}
\begin{document}


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

{\noindent\bf Spring 2023 \hfill First Last}
\vskip 16pt
\centerline{\bf University of Central Florida}
\centerline{\bf College of Business }
\vskip 16pt
\centerline{\bf QMB 6912}
\centerline{\bf Capstone Project in Business Analytics}
\vskip 10pt
\centerline{\bf Problem Set \#4}
\vskip 32pt
\noindent
% 
\section{Data Description}

This analysis follows the script \texttt{Tractor\_Tables.R}. 
The script tabulates various statistics from the variables that may be used to estimate a model for used tractor prices.  
It uses the data from \texttt{TRACTOR7.csv} in the \texttt{Data} folder. 
The dataset includes the following variables.
\begin{table}[h!]
\begin{tabular}{l l l}

$saleprice_i$ & = & the price paid for tractor $i$ in dollars \\
% 
$horsepower_i$ & = & the horsepower of tractor $i$ \\
$age_i$ & = & the number of years since tractor $i$ was manufactured  \\
$enghours_i$ & = & the number of hours of use recorded for tractor $i$  \\
$diesel_i$ & = & an indicator of whether tractor $i$ runs on diesel fuel \\ %, $0$ otherwise \\
$fwd_i$ & = & an indicator of whether tractor $i$ has four-wheel drive \\ %, $0$ otherwise \\
$manual_i$ & = & an indicator of whether tractor $i$ has a manual transmission \\ %, $0$ otherwise \\
$johndeere_i$ & = & an indicator of whether tractor $i$ is manufactured by John Deere \\ %, $0$ otherwise \\
$cab_i$ & = & an indicator of whether tractor $i$ has an enclosed cab \\ %, $0$ otherwise \\
% 
$spring_i$ & = & an indicator of whether tractor $i$ was sold in April or May \\ %, $0$ otherwise \\
$summer_i$ & = & an indicator of whether tractor $i$ was sold between June and September \\ %, $0$ otherwise \\
$winter_i$ & = & an indicator of whether tractor $i$ was sold between December and March \\ %, $0$ otherwise \\

\end{tabular}
\end{table}
%

\bigskip
\noindent
I have downloaded the file {\tt TRACTOR7.csv}, 
loaded the data described above into 
\textsf{R}, 
calculated the summary statistics for these data, 
and finally, presented 
these statistics in \LaTeX\ tables.
These operations are all performed by the script 
{\tt Tractor\_Tables.R} in the {\tt Code} folder. 
The script uses an \textsf{R} package called {\tt xtable} 
to automate the
production of the tables from a data frames in \textsf{R}.)

\medskip
\noindent
I analyze the data in subsets, according to the makes of tractors, 
calculating the summary statistics for each subset and present these 
statistics in the \LaTeX\ tables that follow.

\vfill

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\pagebreak
\section{Summary by Make of Tractors}

Table \ref{tab:summ_by_make} 
lists summary statistics for numeric variables
in separate rows for subsamples defined by the make of tractors, 
according to whether they were manufactured by John Deere. 

\input{../Tables/summ_by_make}


\pagebreak
\section{Indicator Variables by Make of Tractors}

Table \ref{tab:ind_by_make} lists the frequencies of observations of 
each brand of tractor across a series of indicator variables, 
which includes whether a tractor
has a diesel engine, four-wheel-drive transmission, a manual transmission, 
or an enclosed cab to protect the operator.

\input{../Tables/ind_by_make}




\pagebreak
\section{Season Sold by Make of Tractor}

Table \ref{tab:season_sold_by_make} lists the frequencies of observations of 
sales of the brand categories of tractors 
over the four seasons. 


\input{../Tables/season_sold_by_make}







\pagebreak
\section{Correlation Matrices}
To plot the correlation between variables, 
we use the logarithm of prices, which had a better-behaved distribution, 
according to our results in Problem Set \#3.
We separate the analysis into numerical and indicator variables 


Table \ref{tab:correlation_num} shows the correlation 
between the log.~of tractor prices
and the numeric variables horsepower, age and engine hours.


\input{../Tables/correlation_num}


Table \ref{tab:correlation_ind} shows the correlation 
between the log.~of tractor prices
and the indicators for whether a tractor
has a diesel engine, four-wheel-drive transmission, a manual transmission, 
or an enclosed cab to protect the operator. 


\input{../Tables/correlation_ind}


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%


\end{document}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
